Childhood exposure to non-persistent endocrine disruptors, glucocorticosteroids, and attentional function: A cross-sectional study based on the parametric g-formula

### 2024-07-21 output/paper/_si.qmd
Removed vertical and horizontal lines in tables for Epidemiology.

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name) |>
  dplyr::group_by(class) |>
  dplyr::arrange(
    short_name,
    .by_group = TRUE
  )
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Information about non-persistent {{< acr edcs first_use=true >}}, including the full compound name, the standard symbol, the used variable name, the identifier from PubChem, and the parental compound.**
:::

@@

::: {#supptbl-info-mets}
```{r info-mets}
mets_info <- readODS::read_ods(
  path = here::here("docs", "steroids.ods")
) |>
  tidylog::select(analyte, acronym, type, hmdb_id, cas_number) |>
  dplyr::group_by(type) |>
  dplyr::arrange(
    analyte,
    .by_group = TRUE
  )
gt::gt(mets_info,
       groupname_col = "type") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    analyte = "Metabolite",
    acronym = "Symbol",
    hmdb_id = "HMDB ID",
    cas_number = "CAS number"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_footnote(
    footnote = "Abbreviations: Human Metabolome Database (HMDB); Chemical Abstracts Service (CAS).",
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Information about the glucocorticosteroids, including the full metabolite name, the standard symbol, the identifier from the HMDB, and the CAS number.**
:::

@@

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    Metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    LLOQ = "loq"
  ) |>
  tidylog::select(-metabolite) |>
  tidylog::select(Metabolite, LLOQ) |>
  dplyr::arrange(dplyr::desc(LLOQ))
gt::gt(lloq_mets) |>
  gt::tab_footnote(
    footnote = "Abbreviations: lower limit of quantification (LLOQ)."
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    locations = gt::cells_column_labels(),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Lower limits of quantification expressed in ng/ml for the glucocorticosteroids (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  dplyr::left_join(edcs, by = c("exposure" = "chem_id")) |>
  dplyr::select(-exposure) |>
  dplyr::rename(Exposure = "short_name") |>
  dplyr::relocate(Exposure) |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: {{< acr edcs first_use=true >}}; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  dplyr::left_join(edcs, by = c("exposure" = "chem_id")) |>
  dplyr::select(-exposure) |>
  dplyr::rename(Exposure = "short_name") |>
  dplyr::relocate(Exposure) |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: {{< acr edcs first_use=true >}}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::rename(Exposure = "exposure") |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  )
```
**Effective sample size before and after balancing weights estimation (exposures: glucocorticosteroids; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights (exposures: {{< acr edcs first_use=true >}}; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights (exposures: {{< acr edcs first_use=true >}}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: {{< acr edcs first_use=true >}}; outcome: {{< acr hitrtse first_use=true >}}; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  )
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: {{< acr edcs first_use=true >}}; outcomes: glucocorticosteroids; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

>>>>

::: {#supptbl-info-chems}
```{r info-chems}
edcs_info <- myphd::edcs_information() |>
  tidylog::select(-c(chem_id, smiles, ctd_id, exposome_explorer_id)) |>
  tidylog::mutate(
    var = janitor::make_clean_names(
      short_name,
      replace = c(`-` = ""),
      case = "none"
    ) |>
      tolower()
  ) |>
  tidylog::relocate(var, .after = short_name) |>
  dplyr::group_by(class) |>
  dplyr::arrange(
    short_name,
    .by_group = TRUE
  )
gt::gt(edcs_info,
       groupname_col = "class") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    full_name = "Compound",
    short_name = "Symbol",
    var = "Variable name",
    pubchem_cid = "PubChem CID",
    parental_compound = "Parental compound"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Information about non-persistent {{< acr edcs first_use=true >}}, including the full compound name, the standard symbol, the used variable name, the identifier from PubChem, and the parental compound.**
:::

@@

::: {#supptbl-info-mets}
```{r info-mets}
mets_info <- readODS::read_ods(
  path = here::here("docs", "steroids.ods")
) |>
  tidylog::select(analyte, acronym, type, hmdb_id, cas_number) |>
  dplyr::group_by(type) |>
  dplyr::arrange(
    analyte,
    .by_group = TRUE
  )
gt::gt(mets_info,
       groupname_col = "type") |>
  gt::sub_values(
    values = c("NA"),
    replacement = ""
  ) |>
  gt::cols_label(
    analyte = "Metabolite",
    acronym = "Symbol",
    hmdb_id = "HMDB ID",
    cas_number = "CAS number"
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_footnote(
    footnote = "Abbreviations: Human Metabolome Database (HMDB); Chemical Abstracts Service (CAS).",
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Information about the glucocorticosteroids, including the full metabolite name, the standard symbol, the identifier from the HMDB, and the CAS number.**
:::

@@

::: {#supptbl-lloq-mets}
```{r lloq-mets}
lloq_mets <- load_steroids()$loq |>
  tidylog::mutate(
    Metabolite = stringr::str_replace(
      metabolite,
      "^X", ""
    )
  ) |>
  tidylog::rename(
    LLOQ = "loq"
  ) |>
  tidylog::select(-metabolite) |>
  tidylog::select(Metabolite, LLOQ) |>
  dplyr::arrange(dplyr::desc(LLOQ))
gt::gt(lloq_mets) |>
  gt::tab_footnote(
    footnote = "Abbreviations: lower limit of quantification (LLOQ)."
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    locations = gt::cells_column_labels(),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Lower limits of quantification expressed in ng/ml for the glucocorticosteroids (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-balance-1}
```{r balance-1}
balance_1 |>
  dplyr::left_join(edcs, by = c("exposure" = "chem_id")) |>
  dplyr::select(-exposure) |>
  dplyr::rename(Exposure = "short_name") |>
  dplyr::relocate(Exposure) |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Effective sample size before and after balancing weights estimation (exposures: {{< acr edcs first_use=true >}}; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-2}
```{r balance-2}
balance_2 |>
  dplyr::left_join(edcs, by = c("exposure" = "chem_id")) |>
  dplyr::select(-exposure) |>
  dplyr::rename(Exposure = "short_name") |>
  dplyr::relocate(Exposure) |>
  tidylog::group_by(class) |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  tidylog::ungroup() |>
  gt::gt(groupname_col = "class") |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Effective sample size before and after balancing weights estimation (exposures: {{< acr edcs first_use=true >}}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-balance-3}
```{r balance-3}
balance_3 |>
  dplyr::rename(Exposure = "exposure") |>
  dplyr::arrange(dplyr::desc(Adjusted)) |>
  gt::gt() |>
  gt::fmt_number(n_sigfig = 4) |>
  gt::tab_footnote(
    footnote = "Truncated weights.",
    locations = gt::cells_column_labels(columns = Adjusted)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Effective sample size before and after balancing weights estimation (exposures: glucocorticosteroids; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1}
```{r weights-1}
tidy_res_weighted_fits(
  dat_tbl = weights_1$dat_tbl,
  dat_plt = weights_1$dat_plt,
  sa_var = NULL
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Summary statistics of the estimated balancing weights (exposures: {{< acr edcs first_use=true >}}; outcome: {{< acr hitrtse first_use=true >}}) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2}
```{r weights-2}
tidy_res_weighted_fits(
  dat_tbl = weights_2$dat_tbl,
  dat_plt = weights_2$dat_plt,
  sa_var = NULL
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Summary statistics of the estimated balancing weights (exposures: {{< acr edcs first_use=true >}}; outcomes: glucocorticosteroids) (HELIX subcohort; 2013-2016).**
:::

@@

::: {#supptbl-weights-1sa}
```{r weights-1sa}
tidy_res_weighted_fits(
  dat_tbl = weights_1SA$dat_tbl,
  dat_plt = weights_1SA$dat_plt,
  sa_var = "e3_sex"
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: {{< acr edcs first_use=true >}}; outcome: {{< acr hitrtse first_use=true >}}; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

::: {#supptbl-weights-2sa}
```{r weights-2sa}
tidy_res_weighted_fits(
  dat_tbl = weights_2SA$dat_tbl,
  dat_plt = weights_2SA$dat_plt,
  sa_var = "e3_sex"
)$table |>
  gt::tab_row_group(
    label = "OP pesticide metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "OP pesticide metabolites", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phenols",
    rows = variable %in% as.character(edcs[edcs$class == "Phenols", ]$short_name)
  ) |>
  gt::tab_row_group(
    label = "Phthalate metabolites",
    rows = variable %in% as.character(edcs[edcs$class == "Phthalate metabolites", ]$short_name)
  ) |>
  gt::row_group_order(
    groups = c("OP pesticide metabolites",
               "Phenols",
               "Phthalate metabolites")
  ) |>
  gt::tab_style(
    locations = gt::cells_row_groups(group = dplyr::everything()),
    style = list(gt::cell_text(weight = "bold"))
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Summary statistics of the estimated balancing weights for effect modification (exposures: {{< acr edcs first_use=true >}}; outcomes: glucocorticosteroids; modifier: sex) (HELIX subcohort; 2013-2016).**
:::

### 2024-07-21 output/paper/_tables.qmd
Removed vertical and horizontal lines in tables for Epidemiology.

gtsummary::tbl_merge(
  tbls = list(desc_sums_all, desc_sums_intersection)
) |>
  gtsummary::modify_spanning_header(
    dplyr::everything() ~ NA_character_
  ) |>
  gtsummary::as_gt() |>
  gt::tab_footnote(
    footnote = "Measurements available for the HELIX subcohort.",
    locations = gt::cells_column_labels(8)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Participants derived glucocorticosteroids concentrations expressed in ng/ml (HELIX subcohort; 2013-2016).**
:::

@@

dplyr::bind_cols(t1$`_data`, t2$`_data`) |>
  dplyr::select(-`class...4`, -`variable...5`) |>
  dplyr::rename(
    class = "class...1",
    variable = "variable...2"
  ) |>
  dplyr::left_join(
    edcs,
    by = c("variable" = "chem_id")
  ) |>
  dplyr::select(-variable) |>
  dplyr::rename(variable = "short_name") |>
  gt::gt(
    rowname_col = "variable",
    groupname_col = "class"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_footnote(
    footnote = "Estimate and 95% CI.",
    locations = gt::cells_column_labels()
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  )
```
**Pairwise differences between marginal contrasts on the logarithmic scale of males and females, for the effect of a increase from the 10th to the 90th percentile of {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}}, expressed in {{< acr mss >}}, and on the glucocorticosteroids, expressed in ng/ml (HELIX subcohort; 2013-2016).**
:::

>>>>

gtsummary::tbl_merge(
  tbls = list(desc_sums_all, desc_sums_intersection)
) |>
  gtsummary::modify_spanning_header(
    dplyr::everything() ~ NA_character_
  ) |>
  gtsummary::as_gt() |>
  gt::tab_footnote(
    footnote = "Measurements available for the HELIX subcohort.",
    locations = gt::cells_column_labels(8)
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Participants derived glucocorticosteroids concentrations expressed in ng/ml (HELIX subcohort; 2013-2016).**
:::

@@

dplyr::bind_cols(t1$`_data`, t2$`_data`) |>
  dplyr::select(-`class...4`, -`variable...5`) |>
  dplyr::rename(
    class = "class...1",
    variable = "variable...2"
  ) |>
  dplyr::left_join(
    edcs,
    by = c("variable" = "chem_id")
  ) |>
  dplyr::select(-variable) |>
  dplyr::rename(variable = "short_name") |>
  gt::gt(
    rowname_col = "variable",
    groupname_col = "class"
  ) |>
  gt::tab_style(
    style = gt::cell_text(
      weight = "bold"
    ),
    locations = gt::cells_row_groups()
  ) |>
  gt::tab_footnote(
    footnote = "Estimate and 95% CI.",
    locations = gt::cells_column_labels()
  ) |>
  gt::opt_footnote_marks(
    marks = "letters"
  ) |>
  gt::tab_options(
    table_body.hlines.width = 0,
    table_body.vlines.width = 0
  )
```
**Pairwise differences between marginal contrasts on the logarithmic scale of males and females, for the effect of a increase from the 10th to the 90th percentile of {{< acr edcs first_use=true >}} on {{< acr hitrtse first_use=true >}}, expressed in {{< acr mss >}}, and on the glucocorticosteroids, expressed in ng/ml (HELIX subcohort; 2013-2016).**
:::
